Recipient plant traits are important determinants of the impacts of heterospecific pollen upon plant reproduction

### 2019-03-18 Manuscript_draft/Text.Rmd
last edits before sending draft

Matrices of heterospecifc pollen effect and traits (Distance matrix of traits, euclidean distance) are positively and significantly correlated (r=0.4, one-tailed Mantel test p<0.05).The variable/s with maximum rank correlation (thorugh *Bioenv* funtion) was incompatibility index by itself within a group of 16 variables calculated with euclidean distances. The same analysis of Mantel test between heterospecific pollen effect and the traits one by one gave a positive and significant correlation for stigma type and stigma measurements (length, width and area). When the effect of heterospecific pollen was looked at family level, for Solanaceae species we found a positive and significant correlation between heterospecific pollen effect and pollen-ovule ratio
(r=0.74, one-tailed Mantel test p<0.05). Moreover, it seems to be a strong negative correlation between style length and heterospecific pollen effect although lack of significance (Pearson's correlation=0.93, p=0.07) (see **Figure 7**). For Brassicaceae species, the distance matrix of ovules and heterospecic pollen effect gave a positive and significant correlation (r=0.4, one-tailed Mantel test p<0.05).

@@

[explain ratios and total pollen](Jose)
[add table with morphometrical traits to appendix](Jose)

@@

Total pollen deposited on stigmas was significantly correlated with the stigmatic area, pearsons correlation=0.57 and p-value=0.008. Proportions of pollen talk about it to 50-50 mix? Talk aboout this in methods too.

NMDS to appendix?

>>>>

Matrices of heterospecifc pollen effect and traits (Distance matrix of traits, euclidean distance) are positively and significantly correlated (r=0.4, one-tailed Mantel test p<0.05).The variable/s with maximum rank correlation (thorugh *Bioenv* funtion) was incompatibility index by itself within a group of 16 variables calculated with euclidean distances. The same analysis of Mantel test between heterospecific pollen effect and the traits one by one gave a positive and significant correlation for stigma type and stigma measurements (length, width and area). When the effect of heterospecific pollen was looked at family level, for Solanaceae species we found a positive and significant correlation between heterospecific pollen effect and pollen-ovule ratio
(r=0.74, one-tailed Mantel test p<0.05). Moreover, it seems to be a strong negative correlation between style length and heterospecific pollen effect although lack of significance (Pearson's correlation=0.93, p=0.07) (see **Figure 7**). For Brassicaceae species, the distance matrix of ovules and heterospecic pollen effect gave a positive and significant correlation (r=0.4, one-tailed Mantel test p<0.05). Separate to this, the stigmatic area and pollen grain number per stigma were positively correlated, (pearson's correlation=0.57, p<0.01).

@@

add table with morphometrical traits to appendix (Jose)
NMDS to appendix?

@@
